preprocessing

### 2022-12-12 r-prep/prep.Rmd
fix

data_hist_co2=data_cumulative_co2 %>% 
  left_join(dev_status, by= c("country","year")) %>% 
  filter(year <= 2019) %>% 
    mutate(
      EU = country %in% eurostat::eu_countries[2]$name,
      woc = country != "China",
      deving_woc = woc & region_ar6_dev == "developing",
      deved = region_ar6_dev == "developed",
      adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
      adp_region_deving_woc = adp_region_woc & deving_woc
    ) %>% 
  select(-woc)

>>>>

data_hist_co2=data_cumulative_co2 %>% 
  left_join(dev_status, by= c("country","year")) %>% 
  filter(year <= 2019) %>% 
    mutate(
      EU = country %in% eurostat::eu_countries[2]$name,
      woc = country != "China",
      deving_woc = woc & region_ar6_dev == "developing",
      deved = region_ar6_dev == "developed",
      adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
      adp_region_deving_woc = adp_region_woc & deving_woc,
      CO2_FFI = CO2_FFI*1e9
    ) %>% 
  select(-woc)
